Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime

### 2017-06-23 paper.tex
Fixed paper title
Very minor update

\begin{document}
\title{Motional Quantum Ground-State Cooing Outside the Lamb-Dicke Regime}
\author{Yichao Yu}
\author{Nicholas R. Hutzler}
\author{Jessie T. Zhang}
\author{Lee R. Liu}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

The Raman sideband cooling we use to achieve the high ground state preparation fidelity
consists of multiple cycles of laser pulses to manipulate the internal and
motional states of the atoms.
Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
in our setup.
Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
ground electronic state and a certain vibration state $n$.
In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
In the second step, which finishes the cooling cycle,
an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
the entropy via the spontaneously emitted photon.
The second step could also change the motional state of the atoms and result in heating.
The possibility for this to happen for an atom in the motional level $n$
is approximately proportional to the effective Lamb-Dicke (LD) parameter
$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
is the LD parameter for optical pumping, $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.

>>>>

\begin{document}
\title{Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime}
\author{Yichao Yu}
\author{Nicholas R. Hutzler}
\author{Jessie T. Zhang}
\author{Lee R. Liu}
\author{Kang-Kuen Ni}
\email{ni@chemistry.harvard.edu}
\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}

@@

The Raman sideband cooling we use to achieve the high ground state preparation fidelity
consists of multiple cycles of laser pulses to manipulate the internal and
motional states of the atoms.
Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
in our setup.
Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
ground electronic state and a certain vibration state $n$.
In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
In the second step, which finishes the cooling cycle,
an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
the entropy via the spontaneously emitted photon.
The second step could also change the motional state of the atoms and result in heating.
The possibility for this to happen for an atom in the motional level $n$
is approximately proportional to the effective Lamb-Dicke (LD) parameter
$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=k^{OP}\sqrt{\hbar/2m\omega}$
is the LD parameter for optical pumping (OP), $k^{OP}$ is the wavenumber of the OP light, $m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
